---
title: "Get fares data revised"
output: html_notebook
---

```{r}
library(httr)
library(jsonlite)
library(stringr)
library(tidyverse)
library(sf)
library(tmap)
library(stringi)
library(stplanr)
library(lwgeom)
knitr::opts_knit$set(root.dir = "J:/mydocuments/dissertation")
```

Get naptan data:

```{r}
setwd("J:/mydocuments/dissertation")
naptan <- read_csv("naptan/RailReferences.csv")
```

Get file from previous stages of analysis:

```{r}
setwd("J:/mydocuments/dissertation/")
linked_stations <- read_csv("processed_data/msoas_with_linked_stations.csv")
setwd("J:/mydocuments/dissertation/processed_spatial_files")
case_study_stations <- st_read("case_study_stations.shp")
all_trips <- st_read("all_rail_trips_20_08_20.shp")

#tidy the all trips headers
all_trips <- all_trips %>%
  rename(destination = "destntn",
         distance_km = "dstnc_k",
         trip_type = "trp_typ")
```

The fares loop is adapted from a script provided by Young (2020, personal correspondence). Guidance on calculating monthly season ticket prices from 7 day seasons was taken from [railforums.co.uk](https://www.railforums.co.uk/threads/railuk-fares-ticketing-guide-section-5-multi-journey-tickets.67598/). It will also use the following function taken from [Stack Overflow](https://stackoverflow.com/questions/10256503/function-for-median-similar-to-which-max-and-which-min-extracting-median-r)

```{r}
#create which median function ()
whichmedian <- function(x) which.min(abs(x - median(x)))
```

### London fares:
Peak and off-peak fares from the following operators will be excluded, as they offer an infrequent service on the route and services on which the fares could be used were not found.

```{r}
excluded_operators <- c("LBR", "GCR", "HUL")
```

Loop:

```{r}
#Create subset of just the London trips
london_fares <- all_trips %>%
  filter(trip_type == "london_trip") %>%
  select(trip_id, origin, destination) %>%
  st_drop_geometry() %>%
  distinct(trip_id, .keep_all = TRUE)

#set total number of iterations
total <- nrow(london_fares)

#set up errors data frame
errors <- data.frame(
  id = integer(),
  correctOrig = character(),
  correctDest = character(),
  correctRlc = character(),
  noFares = character()
)

for (i in 1:total) {

#set values
  originCrs <- london_fares$origin[i] # is the alternative
  destCrs <- london_fares$destination[i]
  
    # set up the feed URL``
  feedUrl <-
    paste("http://api.brfares.com/queryextra?orig=",
          originCrs,
          "&dest=",
          destCrs,
          sep =
            "")

  # This makes the API call
  req <- GET(feedUrl, config(accept_encoding = "gzip"))  
  
  text <- content(req, as = "text")
  
  # Convert from JSON to list of R objects
  asRlist <- fromJSON(text)

  # Check that the api call response is valid (using the $ signs goes into the levels of the list)
  if (asRlist$correct$orig == TRUE &&
      asRlist$correct$dest == TRUE &&
      asRlist$correct$rlc == TRUE &&
      !is.null(asRlist$fares$adult$fare)) {  
 
  # Define the values of interest (this extracts values from the list)
        fareCategory <- asRlist$fares$category$desc
        routeCode <- asRlist$fares$route$code
        routeName <- asRlist$fares$route$name
        ticketCode <- asRlist$fares$ticket$code
        ticketName <- asRlist$fares$ticket$name
        restrictionCode <- asRlist$fares$restriction$code
        adultFare <- asRlist$fares$adult$fare
        childFare <- asRlist$fares$child$fare
        fareSetter <- asRlist$fares$fare_setter$code
        originName <- asRlist$orig$longname
        destinationName <- asRlist$dest$longname
      
  # Create ticket dataframe
        tickets_tibble <-
          tibble(
            fareCategory,
            routeCode,
            routeName,
            ticketCode,
            ticketName,
            restrictionCode,
            "adultFare" = adultFare / 100,
            "childFare" = childFare / 100,
            fareSetter,
          )
    
    # Subset off-peak returns
    off_peak_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "CDR" |
                     tickets_tibble$ticketCode == "SVR" |
                     tickets_tibble$ticketCode == "BFR" |
                     tickets_tibble$ticketCode == "G2R" |
                     tickets_tibble$ticketCode == "SMG", ] %>%
      filter(!fareSetter %in% excluded_operators)
    
    off_peak_singles <- 
      tickets_tibble[tickets_tibble$ticketCode == "SSS" | #super-offpeak single
                     tickets_tibble$ticketCode == "SOC" | #super-offpeak day single
                     tickets_tibble$ticketCode == "CDS", ] %>%
      filter(!fareSetter %in% excluded_operators)
    
    ## Subset anytime returns
    anytime_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "SDR" |
                     tickets_tibble$ticketCode == "SHR" |
                     tickets_tibble$ticketCode == "SOR" |
                     tickets_tibble$ticketCode == "GOR" |
                     tickets_tibble$ticketCode == "GTR", ] %>%
      filter(!fareSetter %in% excluded_operators)
    
    anytime_singles <- 
      tickets_tibble[tickets_tibble$ticketCode == "SDS" |
                    tickets_tibble$ticketCode ==  "SOS", ] %>%
      filter(!fareSetter %in% excluded_operators)
    
    ## Subset second class seasons
    season_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "PSS" |
                     tickets_tibble$ticketCode == "7DS" | 
                     tickets_tibble$ticketCode == "GF7", ] %>%
      filter(!fareSetter %in% excluded_operators)

    ## Subset second class advance
    advance_tickets <-
      tickets_tibble[tickets_tibble$ticketName == "ADVANCE", ]
    
  # Extract fare - need to take minimum as alternative routes may be possible
    
    ## Get off-peak fare - use CDR if available, otherwise ...
    if (nrow(off_peak_tickets) > 0) {
          if ("CDR" %in% off_peak_tickets$ticketCode) {
            idx <- which.min(off_peak_tickets$adultFare[off_peak_tickets$ticketCode == "CDR"]) #this gets the ID of the cheapest ticket
            offpeakReturn <- off_peak_tickets$adultFare[idx] # which is then extracted (fare)
            offpeakChReturn <- off_peak_tickets$childFare[idx]
            offpeakRestriction <- off_peak_tickets$restrictionCode[idx] #restriction code
            offpeakName <- off_peak_tickets$ticketName[idx]
          } else {
            idx <- which.min(off_peak_tickets$adultFare) #and again
            offpeakReturn <- off_peak_tickets$adultFare[idx]
            offpeakChReturn <- off_peak_tickets$childFare[idx]
            offpeakRestriction <- off_peak_tickets$restrictionCode[idx]
            offpeakName <- off_peak_tickets$ticketName[idx]
                 }
                                     } else 
          if(nrow(off_peak_singles) > 0) {
            idx <- which.min(off_peak_singles$adultFare)
            offpeakReturn <- off_peak_singles$adultFare[idx] * 2
            offpeakChReturn <- off_peak_singles$childFare[idx]  * 2           
            offpeakRestriction <- off_peak_singles$restrictionCode[idx]
            offpeakName <- paste0("Computed from ", off_peak_singles$ticketName[idx])
                                         } else {
            offpeakReturn <- as.numeric("NULL")
            offpeakChReturn <- as.numeric("NULL")
            offpeakRestriction <- as.character("NULL")
            offpeakName <- as.character("NULL")
                                                }
    
    # get anytime fare - use SDR if available, otherwise ...
      if (nrow(anytime_tickets) > 0) {
        if ("SDR" %in% anytime_tickets$ticketCode) {
          idx <-
            which.min(anytime_tickets$adultFare[anytime_tickets$ticketCode == "SDR"])
          anytimeReturn <- anytime_tickets$adultFare[idx]
          anytimeChReturn <- anytime_tickets$childFare[idx]
          anytimeRestriction <- anytime_tickets$restrictionCode[idx]
          anytimeName <- anytime_tickets$ticketName[idx]
                                                   } else {
          idx <- which.min(anytime_tickets$adultFare)
          anytimeReturn <- anytime_tickets$adultFare[idx]
          anytimeChReturn <- anytime_tickets$childFare[idx]
          anytimeRestriction <- anytime_tickets$restrictionCode[idx]
          anytimeName <- anytime_tickets$ticketName[idx]
                                                          }
                                      } else 
        if(nrow(anytime_singles) > 0) {
            idx <- which.min(anytime_singles$adultFare)
            anytimeReturn <- anytime_singles$adultFare[idx] * 2
            anytimeChReturn <- anytime_singles$childFare[idx] * 2            
            anytimeRestriction <- anytime_singles$restrictionCode[idx]
            anytimeName <- paste0("Computed from ", anytime_singles$ticketName[idx])
                                      } else {
          anytimeReturn <- as.numeric("NULL")
          anytimeChReturn <- as.numeric("NULL")
          anytimeRestriction <- as.character("NULL")
          anytimeName <- as.character("NULL")
                                  }
    
    # get monthly season fare - use PSS (monthly) if available, otherwise ...
      if (nrow(season_tickets) > 0) {
        if ("PSS" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "PSS"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1) #round to nearest 10p, as stated in guidance
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1) #round to nearest 10p, as stated in guidance
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  } else 
        if ("7DS" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "7DS"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1)
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1) #round to nearest 10p, as stated in guidance
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  } else
        if ("GF7" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "GF7"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1)
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1) #round to nearest 10p, as stated in guidance
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  }} else {
          monthlySeason <- as.numeric("NULL")
          monthlyChSeason <- as.numeric("NULL")
          monthlyRestriction <- as.character("NULL")
          monthlyName <- as.character("NULL")
                                  }

    # get advance tickets
      if (nrow(advance_tickets) > 0) {
          idx <- whichmedian(advance_tickets$adultFare)
          advanceReturn <- advance_tickets$adultFare[idx] * 2
          advanceChReturn <- advance_tickets$childFare[idx] * 2
          advanceRestriction <- advance_tickets$restrictionCode[idx]
          advanceName <- advance_tickets$ticketName[idx]
      } else {
          advanceReturn <- as.numeric("NULL")
          advanceChReturn <- as.numeric("NULL")          
          advanceRestriction <- as.character("NULL")
          advanceName <- as.character("NULL")                          
                                 }
    
    london_fares[i, "origin_name"] <- originName
    london_fares[i, "destination_name"] <- destinationName
    london_fares[i, "offpeak_fare"] <- offpeakReturn
    london_fares[i, "offpeak_ch_fare"] <- offpeakChReturn
    london_fares[i, "offpeak_restriction"] <- str_trim(offpeakRestriction)
    london_fares[i, "offpeak_name"] <- offpeakName
    london_fares[i, "anytime_fare"] <- anytimeReturn
    london_fares[i, "anytime_ch_fare"] <- anytimeChReturn    
    london_fares[i, "anytime_restriction"] <- str_trim(anytimeRestriction)
    london_fares[i, "anytime_name"] <- anytimeName
    london_fares[i, "season_fare"] <- monthlySeason
    london_fares[i, "season_ch_fare"] <- monthlyChSeason    
    london_fares[i, "season_restriction"] <- str_trim(monthlyRestriction)
    london_fares[i, "season_name"] <- monthlyName
    london_fares[i, "advance_fare"] <- advanceReturn
    london_fares[i, "advance_ch_fare"] <- advanceChReturn    
    london_fares[i, "advance_restriction"] <- str_trim(advanceRestriction)
    london_fares[i, "advance_name"] <- advanceName

  } else {
    # there is a problem with the api call response - record errors in errors dataframe for later review
    newRow <-
      data.frame(
        id = i,
        correctOrig = asRlist$correct$orig,
        correctDest = asRlist$correct$dest,
        correctRlc = asRlist$correct$rlc,
        nofares = paste(is.null(asRlist$fares$adult$fare))
      )
    errors <- rbind(errors, newRow)
  }}
```

### Non-London fares:

```{r}
#subset non-London trips
case_study_area_fares <- all_trips %>%
  filter(trip_type != "london_trip") %>%
  select(trip_id, origin, destination) %>%
  st_drop_geometry() %>%
  distinct(trip_id, .keep_all = TRUE)

#set total number of iterations
total <- nrow(case_study_area_fares)

#set up errors data frame
errors <- data.frame(
  id = integer(),
  correctOrig = character(),
  correctDest = character(),
  correctRlc = character(),
  noFares = character()
)

for (i in 1:total) {

#set values
  originCrs <- case_study_area_fares$origin[i] # is the alternative
  destCrs <- case_study_area_fares$destination[i]
  
    # set up the feed URL``
  feedUrl <-
    paste("http://api.brfares.com/queryextra?orig=",
          originCrs,
          "&dest=",
          destCrs,
          sep =
            "")

  # This makes the API call
  req <- GET(feedUrl, config(accept_encoding = "gzip"))  
  
  text <- content(req, as = "text")
  
  # Convert from JSON to list of R objects
  asRlist <- fromJSON(text)

  # Check that the api call response is valid (using the $ signs goes into the levels of the list)
  if (asRlist$correct$orig == TRUE &&
      asRlist$correct$dest == TRUE &&
      asRlist$correct$rlc == TRUE &&
      !is.null(asRlist$fares$adult$fare)) {  
 
  # Define the values of interest (this extracts values from the list)
        fareCategory <- asRlist$fares$category$desc
        routeCode <- asRlist$fares$route$code
        routeName <- asRlist$fares$route$name
        ticketCode <- asRlist$fares$ticket$code
        ticketName <- asRlist$fares$ticket$name
        restrictionCode <- asRlist$fares$restriction$code
        adultFare <- asRlist$fares$adult$fare
        childFare <- asRlist$fares$child$fare
        fareSetter <- asRlist$fares$fare_setter$code
        originName <- asRlist$orig$longname
        destinationName <- asRlist$dest$longname
      
  # Create ticket dataframe
        tickets_tibble <-
          tibble(
            fareCategory,
            routeCode,
            routeName,
            ticketCode,
            ticketName,
            restrictionCode,
            "adultFare" = adultFare / 100,
            "childFare" = childFare / 100,
            fareSetter
          )
    
    # Subset off-peak returns
    off_peak_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "CDR" |
                     tickets_tibble$ticketCode == "SVR" |
                     tickets_tibble$ticketCode == "BFR" |
                     tickets_tibble$ticketCode == "G2R" |
                     tickets_tibble$ticketCode == "SMG", ]
    
    off_peak_singles <- 
      tickets_tibble[tickets_tibble$ticketCode == "SSS" | #super-offpeak single
                     tickets_tibble$ticketCode == "SOC" | #super-offpeak day single
                     tickets_tibble$ticketCode == "CDS", ]
    
    ## Subset anytime returns
    anytime_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "SDR" |
                     tickets_tibble$ticketCode == "SHR" |
                     tickets_tibble$ticketCode == "SOR" |
                     tickets_tibble$ticketCode == "GOR" |
                     tickets_tibble$ticketCode == "GTR", ]
    
    anytime_singles <- 
      tickets_tibble[tickets_tibble$ticketCode == "SDS" |
                    tickets_tibble$ticketCode ==  "SOS", ]
    
    ## Subset second class seasons
    season_tickets <-
      tickets_tibble[tickets_tibble$ticketCode == "PSS" |
                     tickets_tibble$ticketCode == "7DS" | 
                     tickets_tibble$ticketCode == "GF7", ]
    
    ## Subset second class advance
    advance_tickets <-
      tickets_tibble[tickets_tibble$ticketName == "ADVANCE", ]
    
  # Extract fare - need to take minimum as alternative routes may be possible
    
    ## Get off-peak fare - use CDR if available, otherwise ...
    if (nrow(off_peak_tickets) > 0) {
          if ("CDR" %in% off_peak_tickets$ticketCode) {
            idx <- which.min(off_peak_tickets$adultFare[off_peak_tickets$ticketCode == "CDR"]) #this gets the ID of the cheapest ticket
            offpeakReturn <- off_peak_tickets$adultFare[idx] # which is then extracted (fare)
            offpeakChReturn <- off_peak_tickets$childFare[idx]
            offpeakRestriction <- off_peak_tickets$restrictionCode[idx] #restriction code
            offpeakName <- off_peak_tickets$ticketName[idx]
          } else {
            idx <- which.min(off_peak_tickets$adultFare) #and again
            offpeakReturn <- off_peak_tickets$adultFare[idx]
            offpeakChReturn <- off_peak_tickets$childFare[idx]
            offpeakRestriction <- off_peak_tickets$restrictionCode[idx]
            offpeakName <- off_peak_tickets$ticketName[idx]
                 }
                                     } else 
          if(nrow(off_peak_singles) > 0) {
            idx <- which.min(off_peak_singles$adultFare)
            offpeakReturn <- off_peak_singles$adultFare[idx] * 2
            offpeakChReturn <- off_peak_singles$childFare[idx]  * 2           
            offpeakRestriction <- off_peak_singles$restrictionCode[idx]
            offpeakName <- paste0("Computed from ", off_peak_singles$ticketName[idx])
                                         } else {
            offpeakReturn <- as.numeric("NULL")
            offpeakChReturn <- as.numeric("NULL")
            offpeakRestriction <- as.character("NULL")
            offpeakName <- as.character("NULL")
                                                }
    
    # get anytime fare - use SDR if available, otherwise ...
      if (nrow(anytime_tickets) > 0) {
        if ("SDR" %in% anytime_tickets$ticketCode) {
          idx <-
            which.min(anytime_tickets$adultFare[anytime_tickets$ticketCode == "SDR"])
          anytimeReturn <- anytime_tickets$adultFare[idx]
          anytimeChReturn <- anytime_tickets$childFare[idx]
          anytimeRestriction <- anytime_tickets$restrictionCode[idx]
          anytimeName <- anytime_tickets$ticketName[idx]
                                                   } else {
          idx <- which.min(anytime_tickets$adultFare)
          anytimeReturn <- anytime_tickets$adultFare[idx]
          anytimeChReturn <- anytime_tickets$childFare[idx]
          anytimeRestriction <- anytime_tickets$restrictionCode[idx]
          anytimeName <- anytime_tickets$ticketName[idx]
                                                          }
                                      } else 
        if(nrow(anytime_singles) > 0) {
            idx <- which.min(anytime_singles$adultFare)
            anytimeReturn <- anytime_singles$adultFare[idx] * 2
            anytimeChReturn <- anytime_singles$childFare[idx] * 2            
            anytimeRestriction <- anytime_singles$restrictionCode[idx]
            anytimeName <- paste0("Computed from ", anytime_singles$ticketName[idx])
                                      } else {
          anytimeReturn <- as.numeric("NULL")
          anytimeChReturn <- as.numeric("NULL")
          anytimeRestriction <- as.character("NULL")
          anytimeName <- as.character("NULL")
                                  }
    
    # get monthly season fare - use PSS (monthly) if available, otherwise ...
      if (nrow(season_tickets) > 0) {
        if ("PSS" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "PSS"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1) #round to nearest 10p, as stated in guidance
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1) 
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  } else 
        if ("7DS" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "7DS"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1)
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1) 
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  } else
        if ("GF7" %in% season_tickets$ticketCode) {
          idx <- which.min(season_tickets$adultFare[season_tickets$ticketCode == "GF7"])
          monthlySeason <- round(season_tickets$adultFare[idx] * 3.84, 1)
          monthlyChSeason <- round(season_tickets$childFare[idx] * 3.84, 1)
          monthlyRestriction <- season_tickets$restrictionCode[idx]
          monthlyName <- season_tickets$ticketName[idx]
                                                  }} else {
          monthlySeason <- as.numeric("NULL")
          monthlyChSeason <- as.numeric("NULL")
          monthlyRestriction <- as.character("NULL")
          monthlyName <- as.character("NULL")
                                  }

    # get advance tickets
      if (nrow(advance_tickets) > 0) {
          idx <- whichmedian(advance_tickets$adultFare)
          advanceReturn <- advance_tickets$adultFare[idx] * 2
          advanceChReturn <- advance_tickets$childFare[idx] * 2
          advanceRestriction <- advance_tickets$restrictionCode[idx]
          advanceName <- advance_tickets$ticketName[idx]
      } else {
          advanceReturn <- as.numeric("NULL")
          advanceChReturn <- as.numeric("NULL")          
          advanceRestriction <- as.character("NULL")
          advanceName <- as.character("NULL")                          
                                 }
  
    case_study_area_fares[i, "origin_name"] <- originName
    case_study_area_fares[i, "destination_name"] <- destinationName      
    case_study_area_fares[i, "offpeak_fare"] <- offpeakReturn
    case_study_area_fares[i, "offpeak_ch_fare"] <- offpeakChReturn
    case_study_area_fares[i, "offpeak_restriction"] <- str_trim(offpeakRestriction)
    case_study_area_fares[i, "offpeak_name"] <- offpeakName
    case_study_area_fares[i, "anytime_fare"] <- anytimeReturn
    case_study_area_fares[i, "anytime_ch_fare"] <- anytimeChReturn    
    case_study_area_fares[i, "anytime_restriction"] <- str_trim(anytimeRestriction)
    case_study_area_fares[i, "anytime_name"] <- anytimeName
    case_study_area_fares[i, "season_fare"] <- monthlySeason
    case_study_area_fares[i, "season_ch_fare"] <- monthlyChSeason    
    case_study_area_fares[i, "season_restriction"] <- str_trim(monthlyRestriction)
    case_study_area_fares[i, "season_name"] <- monthlyName
    case_study_area_fares[i, "advance_fare"] <- advanceReturn
    case_study_area_fares[i, "advance_ch_fare"] <- advanceChReturn    
    case_study_area_fares[i, "advance_restriction"] <- str_trim(advanceRestriction)
    case_study_area_fares[i, "advance_name"] <- advanceName


  } else {
    # there is a problem with the api call response - record errors in errors dataframe for later review
    newRow <-
      data.frame(
        id = i,
        correctOrig = asRlist$correct$orig,
        correctDest = asRlist$correct$dest,
        correctRlc = asRlist$correct$rlc,
        nofares = paste(is.null(asRlist$fares$adult$fare))
      )
    errors <- rbind(errors, newRow)
  }}
```

Get one London trip from the range available. Decision based on cheapest advance fare, as this is where variation occurs.

```{r}
london_fares <- london_fares %>%
  arrange(advance_fare) %>%
  distinct(origin, .keep_all = TRUE)

head(london_fares)
```

Now check for missing values in the case study fares. Main thing to check is the season fare:

```{r}
case_study_area_fares %>%
  filter(is.na(season_fare))
```

New Mills Central to Stockport is the only trip that's missing a season. This is likely because there's no direct train. Instead, a fare from New Mills Newtown was manually obtained from BRFares.

```{r}
nmn_spt_season_fare <- 31.30 * 3.84

case_study_area_fares <- case_study_area_fares %>%
  mutate(
    season_fare = case_when(
    origin == "NMC" & destination == "SPT" ~ nmn_spt_season_fare,
                                      TRUE ~ season_fare),
    season_ch_fare = case_when(
    origin == "NMC" & destination == "SPT" ~ nmn_spt_season_fare/2,
                                      TRUE ~ season_ch_fare))
```

```{r}
all_fares <- bind_rows(london_fares, case_study_area_fares)

all_trips <- all_trips %>%
  left_join(all_fares, by = "trip_id")
```

### Write

```{r}
setwd("J:/mydocuments/dissertation/processed_data")
write.csv(all_fares, "all_fares_20_08_20.csv")
```

#### Write up
Fares were obtained from BR Fares (brfares.com)

- http://www.brfares.com/rdg-easier-fares.pdf
- http://www.brfares.com/williams-review.pdf

### Get distance between stations
Network analysis was conducted in ArcGIS Pro to calculate the distance for each trip. To create a dataset that could be used to create a network dataset, the railway line data obtained form Ordnance Survey was edited to join lines together, fill in gaps, and remove overlapping sections in the multilinestring shapefile. The output was then re-processed using the line intersection tool to add junctions. Destination stations were then used as 'facilities' and origins used as 'incidents' during a nearest facility analysis. The results are plotted below.
