---
title: "Preparing Understanding Society data"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(haven)
library(readxl)
library(sjPlot)
library(measurements)
knitr::opts_knit$set(root.dir = "J:/mydocuments/dissertation")
```

This script will process the following variables from Understanding Society wave 8 [(University of Essex et al 2018)](http://doi.org/10.5255/UKDA-SN-6614-13):

```{r linked_understanding_society_fields}
usd_variables <- tibble(
     variable_code = c(
                      "ethn_dv", 
                      "jbsoc10_cc",
                      "jbstat",
                      "worktrav",
                      "jsworktrav",
                      "workdis", 
                      "age_dv",
                      "sex_dv",
                      "ncars",
                      "fimnnet_dv",
                      "fihhmnnet1_dv",
                      "hhsize",
                      "gor_dv",
                      "tenure_dv",
                      "ieqmoecd_dv",
                      "jbft_dv",
                      "jbpl",
                      "jspl",
                      "jbnssec8_dv",
                      "hiqual_dv",
                      "urban_dv",
                      "intdaty_dv",
                      "intdatm_dv"),
     
             name  = c(
                      "Ethnic group (derived from multiple sources)",
                      "Current job: SOC 2010, condensed", 
                      "Current labour force status",
                      "mode of transport for journey to work",
                      "usual mode of transport taken to place of work (self-employed)",
                      "distance from work",
                      "Age, derived from dob_dv and intdat_dv", 
                      "Sex, derived",
                      "number of cars/vans owned by household",
                      "total net personal income - no deductions",
                      "net household monthly income",
                      "number of individuals in the household",
                      "government office region",
                      "housing tenure",
                      "Modified OECD equivalence scale",
                      "Full or part-time employee",
                      "work location",
                      "s/emp:work location",
                      "Current job: Eight Class NS-SEC",
                      "Highest qualification, UKHLS & BHPS samples",
                      "Urban or rural area, derived",
                      "Interview date: Year, derived",
                      "Interview date: Month, derived"),
              
        survey_unit = c(
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "hhresp",
                      "indresp",
                      "hhresp",
                      "hhresp",
                      "indresp",
                      "hhresp",
                      "hhresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp",
                      "indresp"),
     
             waves = c("all",
                       "all",
                       "all",
                       "all",
                       "1, 2, 4, 6, 8",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all",
                       "all"),
     
             type = c(
                      "constraint", 
                      "constraint", 
                      "constraint", 
                      "constraint", 
                      "constraint",
                      "constraint", 
                      "constraint", 
                      "constraint", 
                      "constraint", 
                      "target", 
                      "target", 
                      "target",
                      "filter variable",
                      "constraint",
                      "target",
                      "constraint",
                      "constraint",
                      "constraint",
                      "constraint",
                      "constraint",
                      "constraint",
                      "admin",
                      "admin"),

             link = c(
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ethn_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbsoc10_cc",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbstat",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/worktrav",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jsworktrav",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/workdis",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/age_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/sex_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncars",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fimnnet_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fihhmnnet1_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/hhsize",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/gor_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/tenure_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ieqmoecd_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbft_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbpl",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jspl",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/jbnssec8_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/hiqual_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/urban_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/intdaty_dv",
                      "https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/intdatm_dv"))

usd_variables
```

Individual response data:

```{r get understanding society data for individuals}
#get wave 9
ind_wave_8 <- read_spss("understanding_society/UKDA-6614-spss/spss/spss24/ukhls_w8/h_indresp.sav")
```

Make a vector of variable names:

```{r}
ind_var_codes_vec <- usd_variables %>%
  filter(survey_unit == "indresp") %>% #all the individual response codes from the table above
  select(variable_code) %>%
  mutate(variable_code = paste0("h_", variable_code, sep = "")) %>%
  as_vector() %>%
  c("pidp", "h_hidp") %>% #the UID codes
  unname()
```

Subset the full response table, to obtain just the variables of interest:

```{r}
ind_subset <- subset(ind_wave_8, select = ind_var_codes_vec) %>%
  select(pidp, h_hidp, everything())
```

Summarise each value, and tally missings:

```{r}
list <- map(ind_subset %>% select(-pidp, -h_hidp) %>% names() %>% set_names(),
          ~ ind_subset %>%
            as_factor(only_labelled = TRUE) %>%
            group_by_at(.x) %>%
            summarise(Count = n()))

list

#show all the labels for each of the columns we are working with ...
sjPlot::view_df(ind_subset, max.len = 100)

list$h_jbstat %>%
  filter(!h_jbstat %in% c("Self employed", "Paid employment(ft/pt)")) %>%
  summarise(sum(Count))

```

'Missing' fields are -9 (missing), -7 (proxy, where this question isn't asked), -2 (refusal), and -1 (don't know). Inapplicable (-8), is a bit more complicated. It often means that a person can't respond to the question. A response may be imputed from another variable.

Create a vector of NA values:

```{r}
#lots of text in amongst the numeric values ...
na_values_vec <- c("missing", "inapplicable", "proxy", "refusal", "don't know")
```

Create economic_activity field:

```{r}
ind_subset <- ind_subset %>% mutate(
                              h_jbstat = as.character(as_factor(h_jbstat)),
                              h_jbft_dv = as.character(as_factor(h_jbft_dv)),
                              economic_activity = case_when(
                                h_jbstat == "Self employed" ~ "self_employed",
                               h_jbft_dv ==  "PT employee"  ~ "part_time",
                               h_jbft_dv ==  "FT employee"  ~ "full_time"
                              ))
```

Filter out people not in employment:

```{r}
ind_subset <- ind_subset %>% filter(economic_activity %in% c("self_employed", "part_time", "full_time"))

#create a lookup table
travel_to_work_lookup <- tibble(
  usd = c("Get a lift with someone outside the household",
          "Get a lift with someone from household",
          "Underground/Metro/Tram/Light railway",
          "Drive myself by car or van",
          "Motorcycle/moped/scooter",
          "Taxi/minicab",
          "Bus/coach",
          "Train",
          "Cycle",
          "Walk",
          "Other"),
  
census = c("passenger_in_a_car",
           "passenger_in_a_car",
           "metro_light_rail_etc",
           "driving_a_car",
           "motorcycle",
           "taxi",
           "bus",
           "train",
           "bicycle",
           "on_foot",
           "other"))

travel_to_work_lookup

#create a vector for matching ...
travel_to_work_lookup_vec <- 
  setNames(travel_to_work_lookup$census, travel_to_work_lookup$usd)

mobile_worker_categories <- c("From a van or stall", "Driving or travelling around", "From client's or customer's premises", "Or at one or more other places?")


ind_subset %>% filter(economic_activity == "Self employed")

#convert the relevant fields to characters
ind_subset <- ind_subset %>%
  mutate(
    h_jbpl = as.character(as_factor(h_jbpl)),
    h_jspl = as.character(as_factor(h_jspl)),
    h_worktrav = as.character(as_factor(h_worktrav)),
    h_jsworktrav = as.character(as_factor(h_jsworktrav)))

#set new categorical field
ind_subset <- ind_subset %>%
  mutate(method_of_travel_to_work =
           case_when(
         h_jbpl %in% c("At home", "From their own home")           ~ "work_from_home_ttw",
         h_jspl %in% c("At home", "From their own home")           ~ "work_from_home_ttw",
                       h_jbstat == "Paid employment(ft/pt)"        ~ travel_to_work_lookup_vec[h_worktrav],
                       h_jbstat == "Self employed"                 ~ travel_to_work_lookup_vec[h_jsworktrav]))

ind_subset <- ind_subset %>%
  mutate(                                            
         method_of_travel_to_work =                  #find travel to work values for self-employed from the non-se ttw field
           if_else(is.na(method_of_travel_to_work) &
                       h_jbstat == "Self employed" &
                     !h_worktrav %in% na_values_vec, #then 
             travel_to_work_lookup_vec[h_worktrav], method_of_travel_to_work),
         
         method_of_travel_to_work =                  #find travel to work values for normal employed from the se ttw field
           if_else(is.na(method_of_travel_to_work) & 
                       h_jbstat == "Paid employment(ft/pt)" &
                     !h_jsworktrav %in% na_values_vec, #then 
             travel_to_work_lookup_vec[h_jsworktrav], method_of_travel_to_work),

        method_of_travel_to_work =                   #find wfh values for se in non-se workplace field
          if_else(is.na(method_of_travel_to_work) &
                      h_jbstat == "Self employed" &
                     h_jbpl %in% c("At home", "From their own home"), #then
                                "work_from_home_ttw", method_of_travel_to_work),
        
        method_of_travel_to_work =                   #find wfh values for non-se in se workplace field
          if_else(is.na(method_of_travel_to_work) &
                      h_jbstat == "Paid employment(ft/pt)" &
                     h_jspl %in% c("At home", "From their own home"), #then
                                "work_from_home_ttw", method_of_travel_to_work)) %>%
  
    mutate(method_of_travel_to_work = case_when(     #replace 'other' with NA
      method_of_travel_to_work == "other" ~ as.character(NA),
                                     TRUE ~ method_of_travel_to_work
  ))

```

Work distance:

```{r}
#create a new field which just takes the non-na values from the main survey column, and replaces 
#this with a numeric value for the distance. 0s go to people who work from home. Others resolve to NA.

ind_subset <- ind_subset %>%
  mutate(
    distance_to_work_miles = case_when(
                             method_of_travel_to_work == "work_from_home_ttw" ~ as.numeric(0),
                                     h_workdis %in% c(-9, -8, -7, -2, -1) ~ as.numeric(NA),
                                                                     TRUE ~ as.numeric(h_workdis)))

#looks good. Now convert to km
ind_subset <- ind_subset %>%
  mutate(
    distance_to_work_km = round(conv_unit(distance_to_work_miles, "mi", "km"), 1))

#and check ...
ind_subset %>%
  select(distance_to_work_miles, h_workdis, distance_to_work_km)

#now bin it, based on the values given in the census
distance_travelled_to_work_agg <- read_csv("census/nomis/distance_travelled_to_work.csv")

distance_travelled_to_work_agg[6:17] %>%
  colnames() %>%
  as_tibble()

ind_subset <- ind_subset %>%
  mutate(distance_category = case_when(
    method_of_travel_to_work == "work_from_home_ttw" ~ "work_from_home_distance",
    distance_to_work_km <2 ~ "less_than_two_km",
    distance_to_work_km <5 ~ "two_to_less_than_five",
    distance_to_work_km <10 ~ "five_to_less_than_ten",
    distance_to_work_km <20 ~ "ten_to_less_than_twenty",
    distance_to_work_km <30 ~ "twenty_to_less_than_thirty",
    distance_to_work_km <40 ~ "thirty_to_less_than_forty",
    distance_to_work_km <60 ~ "forty_to_less_than_sixty",
    distance_to_work_km >= 60 ~ "more_than_sixty"))
```

NS-SEC:

```{r}
ind_subset <- ind_subset %>%
  mutate(
    h_jbnssec8_dv = as.character(as_factor(h_jbnssec8_dv)),
    ns_sec_category = 
    case_when(
      h_jbnssec8_dv == "Large employers & higher management" ~ "one",
      h_jbnssec8_dv == "Higher professional" ~ "one",
      h_jbnssec8_dv == "Lower management & professional" ~ "two",
      h_jbnssec8_dv == "Intermediate" ~ "three",
      h_jbnssec8_dv == "Small employers & own account" ~ "four",
      h_jbnssec8_dv == "Lower supervisory & technical" ~ "five",
      h_jbnssec8_dv == "Semi-routine" ~ "six",
      h_jbnssec8_dv == "Routine" ~ "seven"))

```

Age:

```{r}
#compare census and usd ...
ns_sec_by_sex_by_age <- read_csv("census/nomis/ns_sec_by_sex_by_age.csv")

#create banded variable ...
ind_subset <- ind_subset %>%
  mutate(
        h_age_dv = as.numeric(as.character(as.factor(h_age_dv))), #convert to numeric from SPSS factor
     age_banding = case_when(
        h_age_dv %in% c(-9, -8, -2, -1) ~ as.character(NA),
                         h_age_dv < 25  ~ "16_24",
                         h_age_dv < 35  ~ "25_34",
                         h_age_dv < 50  ~ "35_49",
                         h_age_dv < 65  ~ "50_64",
                         h_age_dv < 103 ~ "65_plus"))
```

Create age and sex variable:

```{r}
ind_subset <- ind_subset %>% mutate(
                  sex = case_when(
                               as.character(as_factor(h_sex_dv)) == "Female" ~ "f",
                               as.character(as_factor(h_sex_dv)) == "Male" ~ "m"),
              age_sex = case_when(
                               sex %in% c("f", "m") ~ paste0(sex, "_", age_banding)))
```

Ethnic group (categories taken from: https://www.researchgate.net/publication/321243183_Microsimulation_for_demography):

```{r}
#get census data for category matching ... 
ethnic_group_agg <- read_csv("census/nomis/ethnic_group.csv")

ethnic_group_agg %>%
  colnames()

#check usd data ...
ind_subset %>%
  group_by(h_ethn_dv) %>%
  tally() %>%
  mutate(
    percent_of_total = round((n / sum(n))*100, 1)
  ) %>%
  arrange(desc(percent_of_total))

#create a lookup table ...
ethnicity_conversion_table <- tibble(
  super_condensed_category = c(
                      "asian",
                      "black",
                      "black",
                      "asian",
                      "asian",
                      "mixed",
                      "mixed",
                      "mixed",
                      "mixed",
                      "asian",
                      "black",
                      "other",
                      "other",
                      "asian",
                      "white",
                      "white",
                      "white",
                      "white"),
  
  condensed_category = c(
                      "Bangladeshi",
                      "Black African",
                      "Black Caribbean",
                      "Chinese",
                      "Indian",
                      "Mixed",
                      "Mixed",
                      "Mixed",
                      "Mixed",
                      "Other Asian",
                      "Other Black",
                      "Other",
                      "Other",
                      "Pakistani", 
                      "White British", 
                      "White Other",
                      "White Other",
                      "White Other"),
  
  cenesus_categories = c(
                      "Asian/Asian British: Bangladeshi", 
                      "Black/African/Caribbean/Black British: African", 
                      "Black/African/Caribbean/Black British: Caribbean",
                      "Asian/Asian British: Chinese",
                      "Asian/Asian British: Indian",
                      "Mixed/multiple ethnic groups: White and Black Caribbean", 
                      "Mixed/multiple ethnic groups: White and Black African",
                      "Mixed/multiple ethnic groups: White and Asian",
                      "Mixed/multiple ethnic groups: Other",
                      "Asian/Asian British: Other",
                      "Black/African/Caribbean/Black British: Other Black",
                      "Other ethnic group: Arab",
                      "Other ethnic group: Any other ethnic group",
                      "Asian/Asian British: Pakistani",
                      "White: English/Welsh/Scottish/Northern Irish/British",
                      "White: Irish",
                      "White: Gypsy or Irish Traveller",
                      "White: Other White"),
  
  usd_categories = c(
                      "bangladeshi",
                      "african",
                      "caribbean",
                      "chinese",
                      "indian",
                      "white and black caribbean",
                      "white and black african",
                      "white and asian",
                      "any other mixed background",
                      "any other asian background",
                      "any other black background",
                      "arab",
                      "any other ethnic group",
                      "pakistani",
                      "british/english/scottish/welsh/northern irish",
                      "irish",
                      "gypsy or irish traveller",
                      "any other white background"
                    ))

#create a lookup vector to use for matching and returning values ...
usd_condensed_ethnicity_lookup <- 
  setNames(ethnicity_conversion_table$condensed_category, ethnicity_conversion_table$usd_categories)

#convert from Haven labelled ...
ind_subset <- ind_subset %>%
              mutate(
                    h_ethn_dv = as.character(as_factor(h_ethn_dv)),
                    condensed_ethnicity = usd_condensed_ethnicity_lookup[as.character(h_ethn_dv)])
```
```{r}
usd_super_condensed_ethnicity_lookup <- 
  setNames(ethnicity_conversion_table$super_condensed_category, ethnicity_conversion_table$usd_categories)

ind_subset <- ind_subset %>%
              mutate(
                    super_condensed_ethnicity = usd_super_condensed_ethnicity_lookup[as.character(h_ethn_dv)])
```

Case study region field (region is one of East Midlands, North West, Yorkshire and the Humber):

```{r}
regions_vec <- c("North West", "Yorkshire and the Humber", "East Midlands")

ind_subset <- ind_subset %>%
  mutate(region = case_when(
    h_gor_dv %in% c(-9, -8, -2, -1) ~ as.character(NA),
                               TRUE ~ as.character(as_factor(h_gor_dv))),
    
         region_category = case_when(
            region %in% regions_vec ~ "From case study regions",
                               TRUE ~ "Not from case study regions"))
```

### Highest level of qualification
Census provides a 6 stage linked variable. See: https://www.gov.uk/what-different-qualification-levels-mean/list-of-qualification-levels Range of usd options available. Summary here: https://iserswww.essex.ac.uk/support/issues/337

```{r}
highest_qual_agg <- read_csv("census/nomis/highest_level_of_qualification.csv")

highest_qual_agg %>%
  colnames() %>%
  as_tibble()

quals_lookup <- tibble(
  category = c("Level 4 plus", "Level 4 plus", "Level 3", "Level 1 and Level 2", "No qualifications", "Other qualifications"),
  usd_value = c("Degree", "Other higher degree", "A-level etc", "GCSE etc", "No qualification", "Other qualification"))

ind_subset <- ind_subset %>%
  mutate(highest_qualification = case_when(
                                 h_hiqual_dv %in% c(-9, -8, -2, -1) ~ as.character(NA),
                                                               TRUE ~ as.character(as_factor(h_hiqual_dv))),
         highest_qual_category = case_when(
                                 highest_qualification %in% c("Degree", "Other higher degree") ~ "level_four_plus",
                                 highest_qualification == "A-level etc" ~ "level_three",
                                 highest_qualification == "GCSE etc" ~ "level_one_or_level_two",
                                 highest_qualification == "No qualification" ~ "no_qualification",
                                 highest_qualification == "Other qualification" ~ "other_qualification"))
```

Urban/rural:

```{r}
ind_subset <- ind_subset %>% mutate(
      urban_rural = case_when(
        h_urban_dv %in% c(-9, -8, -2, -1) ~ as.character(NA),
                                     TRUE ~ as.character(as_factor(h_urban_dv))),
      urban_rural = case_when(urban_rural == "urban area" ~ "urban",
                              urban_rural == "rural area" ~ "rural"))
```

Month/date of interview:

```{r}
ind_subset <- ind_subset %>%
  mutate(
    interview_month = as.numeric(as.character(as_factor(h_intdatm_dv))),
    interview_year = as.numeric(as.character(as_factor(h_intdaty_dv))),
    interview_month_and_year = paste0(interview_month, "_", interview_year))
```

Income: We need to convert this from haven and then equivilise to 2019 values. Equivilisation advice from [(Fisher et al 2019, p.27)](https://www.understandingsociety.ac.uk/sites/default/files/downloads/working-papers/2019-08.pdf). Index from 'Consumer Price Indices series excluding rents, maintenance repairs and water charges' (see [ONS 2020](https://www.ons.gov.uk/economy/inflationandpriceindices/adhocs/11357consumerpriceindicesseriesexcludingrentsmaintenancerepairsandwaterchargesfortheperiodjanuary1996todecember2019)).

```{r}
ind_subset <- ind_subset %>%
  mutate(
          personal_income = as.numeric(as.character(as_factor(h_fimnnet_dv))),   #convert from haven
          personal_income = case_when(                                           #catch the negative values (outliers)
                              personal_income < 0 ~ as.numeric(NA),
                                             TRUE ~ personal_income))
#get index
index_orig <- read.csv("adjust_income/dwp_deflators_feb_2020_csv.csv")

#tidy it
index <- index_orig %>%
  mutate(
    year = as.numeric(str_sub(Index.Date, 1, 4)),
    month = as.numeric(str_sub(Index.Date, -2, -1)),
    interview_month_and_year = paste0(month, "_", year),
    index_base_2015 =  CPI.Index..2015...100.
  ) %>%
  as_tibble() %>%
  select(interview_month_and_year, index_base_2015)

dec_2019_index <- index %>% filter(interview_month_and_year == "12_2019") %>%
  pull(index_base_2015)

ind_subset <- ind_subset %>%
  left_join(index, by = "interview_month_and_year")

ind_subset <- ind_subset %>%
  mutate(personal_income = personal_income * (dec_2019_index / index_base_2015), #rebase
         personal_income = round(personal_income, 0)) #round
```

Get household dataset:

```{r get understanding society data for households}
hh_wave_8 <- read_spss("understanding_society/UKDA-6614-spss/spss/spss24/ukhls_w8/h_hhresp.sav")

hh_wave_8 %>% glimpse()

hh_var_codes_vec <- usd_variables %>%
                    filter(survey_unit == "hhresp") %>%
                    select(variable_code) %>%
                    mutate(variable_code = paste0("h_", variable_code, sep = "")) %>%
                    as_vector()

hh_admin_var_codes <- "h_hidp"

hh_subset <- subset(hh_wave_8, select = c(hh_var_codes_vec, hh_admin_var_codes)) %>%
             select(h_hidp, everything())

#show all the labels for each of the columns we are working with ...
sjPlot::view_df(hh_subset, max.len = 100)

hh_subset

```

Number of cars:

```{r car categorical}
hh_subset <- hh_subset %>%
             mutate(hh_number_of_cars = as.numeric(as.character(as_factor(h_ncars))),
                    hh_cars_category = case_when(
                      hh_number_of_cars == 0 ~ "no_cars",
                      hh_number_of_cars == 1 ~ "one_car",
                      hh_number_of_cars >= 2 ~ "two_or_more_cars"))
#Check the breakdown ...
hh_subset %>%
  group_by(hh_cars_category) %>%
  tally() %>%
  mutate(
    percent_of_total = round((n / sum(n))*100, 1)) %>%
  arrange(desc(percent_of_total))
```

Tenure:

```{r tenure}
tenure_agg <- read_csv("census/nomis/tenure.csv")

tenure_agg %>% colnames()

hh_subset <- hh_subset %>% mutate(
         h_tenure_dv = as.character(as_factor(h_tenure_dv)),
    tenure_condensed = case_when(
       h_tenure_dv %in% c("Local authority rent", "Housing assoc rented")                                   ~ "social_rented",
       h_tenure_dv %in% c("Rented from employer", "Rented private unfurnished", "Rented private furnished") ~ "private_rented",
       h_tenure_dv %in% c("Owned outright", "Owned with mortgage")                                          ~ "owned"))

hh_subset %>%
  group_by(tenure_condensed) %>%
  tally() %>%
  mutate(
    percent_of_total = round((n / sum(n))*100, 1)) %>%
  arrange(desc(percent_of_total))

```

Income, OECD conversion data and household size fields:

```{r}
hh_subset <- hh_subset %>% mutate(
                            household_income = case_when(
                                      h_fihhmnnet1_dv %in% c(-9 ,-8, -2, -1) ~ as.numeric(NA),
                                                         h_fihhmnnet1_dv < 1 ~ as.numeric(NA),
                                                                        TRUE ~ as.numeric(as.character(as_factor(h_fihhmnnet1_dv)))),
                            household_income = round(household_income, 0),
                      oecd_equivilance_scale = case_when(
                                    h_ieqmoecd_dv %in% c(-9 ,-8, -7, -2, -1) ~ as.numeric(NA),
                                                                        TRUE ~ as.numeric(as.character(as_factor(h_ieqmoecd_dv)))))

```

Household size:

```{r}
hh_subset <- hh_subset %>% mutate(
  household_size = h_hhsize)
```

Merge of the individual and household responses: 

```{r join to individual response table}

glimpse(hh_subset)

usd_microdata <- ind_subset %>%
  select(                     #select fields from the ind table ...
    pidp,
    h_hidp,
    method_of_travel_to_work,
    distance_to_work_km,
    distance_category,
    ns_sec_category,
    age_banding,
    age_sex,
    condensed_ethnicity,
    super_condensed_ethnicity,
    region,
    region_category,
    personal_income,
    highest_qual_category,
    economic_activity,
    urban_rural,
    interview_month_and_year,
    index_base_2015
    ) %>%
  left_join(
    hh_subset %>%                  
      select(                   #now select fields from the hh table ...
        h_hidp,
        hh_number_of_cars,
        hh_cars_category,
        tenure_condensed,
        household_income,
        oecd_equivilance_scale,
        household_size
        ), by = "h_hidp")
```

Adjust hosuehold income to 2019 prices:

```{r}
usd_microdata <- usd_microdata %>%
        mutate(household_income = household_income * (dec_2019_index / index_base_2015), #rebase
               household_income = round(household_income, 0), #round
              oecd_eq_hh_income = round(household_income / oecd_equivilance_scale, 0))
```

We've got 266 respondents who don't appear to be linked with household. We can mark those on the main dataset, just so we're aware of where they've come from:

```{r prove lack of link on household variables for certain cases}
no_hh_match_vec <- anti_join(ind_subset, hh_subset, by = "h_hidp") %>%
                   select(pidp) %>%
  mutate(pidp = as.numeric(pidp)) %>%
                    as_tibble() %>%
                       unname()

names(no_hh_match_vec) <- "pidp"

no_hh_match_vec <- no_hh_match_vec %>%
  pull()

usd_microdata <- usd_microdata %>%
  mutate(
    missing_hh_match = case_when(
      pidp %in% no_hh_match_vec ~ as.character(TRUE),
                           TRUE ~ as.character(FALSE)))

usd_microdata %>%
  filter(missing_hh_match == "TRUE")
```

Summarise the NAs (advice taken from here: https://sebastiansauer.github.io/sum-isna/):

```{r count NAs}
#by variable ...
usd_microdata %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.)))) %>%
  gather(variable_name, total_nas)

#by case ...
count_na <- function(x) sum(is.na(x))

usd_microdata <- usd_microdata %>%        #add a count to each case of the number of NAs it includes
  mutate(
    case_nas = apply(., 1, count_na))

usd_microdata %>%
  group_by(case_nas) %>%
  tally()
```

Count nas at different stages:

```{r}
usd_microdata %>%
  mutate(reason_for_exclusion = case_when(
    missing_hh_match == "TRUE" ~ "1. No household match",
    is.na(method_of_travel_to_work) ~ "2. Non response to a transport question",
    is.na(distance_to_work_km) ~ "2. Non response to a transport question",
    case_nas >= 1 ~ "3. Other non-response",
    TRUE ~ "Included in final data"
  )) %>%
  group_by(reason_for_exclusion) %>%
  tally()
```

Filter, count and export:

```{r filter, count and export}
usd_microdata %>%
  filter(case_nas == 0) %>%
  select(-missing_hh_match, -case_nas) %>%
  write_csv("processed_data/usd_microdata/usd_microdata_processed_13_08_20b.csv")

map(usd_microdata %>% names() %>% set_names(),
          ~ usd_microdata %>%
            group_by_at(.x) %>%
            summarise(Count = n()))
```


Additional references and notes:

- Helpful collection of articles on dealing with survey data: https://www.r-bloggers.com/working-with-spss-labels-in-r/
- Good instructions on summarising datasets: https://datacarpentry.org/R-genomics/04-dplyr.html